Quasi-Monte Carlo Methods: What, Why, and How?

### 2025-01-08 HickernellMCQMC2024_QMCTutorial.tex
M2 Mac updates

	\item \emph{Low discrepancy nodes.}  For qMC methods the error decays nearly like $\mathcal{O}(n^{-1})$, which for this example correponds to a reduction in error of several orders of magnitude for large enough $n$.  Typically, low discrepancy sequences have preferred sample sizes.  For this Sobol' sequence, $n$ a positive integer power of $2$ tends to give better accuracy than arbitrary $n$.

>>>>

	\item \emph{Low discrepancy nodes.}  For qMC methods the error decays nearly like $\mathcal{O}(n^{-1})$, which for this example correponds to a reduction in error of several orders of magnitude compared to simple MC for large enough $n$.  Typically, low discrepancy sequences have preferred sample sizes.  For this Sobol' sequence, $n$ equal to a positive integer power of $2$ tends to give better accuracy than arbitrary $n$.
